The \dealii{} Library, Version 9.3

### 2021-06-21 9.3/paper.tex
Reword the ReferenceCell section.
'instantiated' isn't quite right here because this is a glorified enum (not a
template class). I had to rearrange a sentence to avoid things spilling into
margins.

Geometric information about cells and faces -- previously provided by
the \texttt{GeometryInfo} class for hypercube-type cells -- is now
available via the  \texttt{ReferenceCell} class that can be
instantiated for each of the seven possible reference cell. The
correct reference cell object for a cell or face can be obtained, respectively, using
\texttt{cell->reference\_cell()}, and either the call
\texttt{cell->reference\_cell().face\_reference\_cell(f)}
or
\texttt{cell->face(f)->reference\_cell()}.

>>>>

Geometric information about cells and faces -- previously provided by
the \texttt{GeometryInfo} class for hypercube-type cells -- is now
available via the \texttt{ReferenceCell} class that is defined
for each of the seven possible reference cells. The correct
\texttt{ReferenceCell} for a cell or face can be obtained,
respectively, using
\texttt{cell->reference\_cell()}, and either
\texttt{cell->face(f)->reference\_cell()}
or
\texttt{cell->reference\_cell().face\_reference\_cell(f)}.
